Composable Concurrency Abstractions

### 2016-09-13 annotated-bibliography/annotated-bibliography.tex
Brought bibliography in line with UMM style

\documentclass[12pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}

\author{Dan Stelljes}
\date{September 15, 2016}
\title{Annotated Bibliography}

@@

\maketitle
\nocite{*}

\bibliographystyle{annotate}
\bibliography{references}

>>>>

\documentclass{sig-alternate}
\usepackage{url}

\author{
\alignauthor{}
Dan Stelljes\\
  \affaddr{Division of Science and Mathematics}\\
  \affaddr{University of Minnesota, Morris}\\
  \affaddr{Morris, Minnesota, USA 56267}\\
  \email{stell124@morris.umn.edu}
}
\conferenceinfo{UMM CSci Senior Seminar Conference, December 2016}{Morris, MN}
\title{Composable Concurrency Abstractions}
\subtitle{Annotated Bibliography}

@@

\maketitle

\begin{abstract}
A wide variety of concurrency models presents challenges in both performance and composability. By identifying common concepts and techniques, a high-level language virtual machine can support a variety of abstractions at a low level, and different models can be used in tandem with each other.
\end{abstract}

\nocite{*}

\bibliographystyle{abbrv}
\bibliography{references}
